---
title: "2019statcacul"
author: "HolaTeo"
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
  html_document:
    df_print: paged
  pdf_document:
    latex_engine: xelatex
  word_document: default
mainfont: NanumGothic
---
install.packages("foreach")
install.packages("tidyverse")

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

```{r Tidyverse, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(dplyr)
library(foreach)
```

#Q1
##
```{r coin}
coin <- function(prob=0.3, bet=1, Pe = 6, Pa = 4){
 rec <- tibble(a = Pe, b = Pa)
 while(all(rec>0)){
    u <- runif(1)
   Pe <- ifelse(u<prob, Pe+bet,Pe-bet)
   Pa <- ifelse(u>=prob, Pa+bet,Pa-bet)
   rec <- rec %>% bind_rows(c(a=Pe, b=Pa))
   if(Pe==0 | Pa==0) break() 
 }
 rec %>% mutate(idx = 1:n())  %>%
   select(a, b) %>% 
   summarise(Gamesu=n(), who_win=ifelse(last(a)==0, "Paul Win!","Peter Win!"), PeterMoney=mean(a))
}

(resault <- coin(prob=0.3, bet=1, Pe=6, Pa=4))
```

##
```{r coin2}

rep <- foreach(i=1:1000, .combine = bind_rows) %do%
               {
                 coin()
} %>% 
  summarise(Peter_Win_Prob=mean(who_win=="Peter Win!"),Game_Time=mean(Gamesu),Peter_Money_Mean=mean(PeterMoney))

(resault2 <- rep)
```

#Q2

project 6.B
correlation : pearson corr & spearman
H0 : rho=0 이 참일 때 rho.hat들의 분포를 찾음

$Corr($ $X_1, ... , X_n$, sample(c($Y_1,...,Y_n$)))

library(mvtnorm)

n<-20
m<-1000
rho0 <- 0
rho <- c(seq(-1,1,length=40)) #alternative
M <- length(rho)
power1 <-
power2 <-
power3 <-

rhotest <- cor.test(samp[,1], samp[,2], method="pearson", rhotest$p.value)
        <- cor.test(samp[,1], samp[,2], method="kendal", rhotest$p.value)

plot(rho, power1, type="l")
lines(rho, power2, lty=1)
lines(rho, power3, lty=2)


#Q3

##
```{r MCBase}
m<-10000
mc <- function(m){
x <-rcauchy(m)
fg <- as.numeric(x>2)
a1 <- mean(fg)
return(a1)
}
mc(m)
```

##important sampling
```{r important1}
mc.impo1 <- function(m){
x<-2/runif(m)
fg <- 1/(2*(pi*(1+1/x^2)))
b1 <- mean(fg)
return(b1)
}
mc.impo1(m)
```


### important sampling2
```{r impotant2}
mc.impo2 <- function(m){
x<-runif(m, 0, 0.5)
fg <- dcauchy(x)/2
b2<-mean(fg)
return(b2)
}
mc.impo2(m)
```


##hit or miss
```{r hit}
mc.hit <- function(m){
x <- runif(m, 0, 2)
y <- runif(m, min=0, max=dcauchy(0))
est <- 1/2 - sum(as.numeric(y<=dcauchy(x)))/m*(2*dcauchy(0)) #2*decauchy(0)은 전체 면적,sum(as.numeric(y<=dcauchy(0)))/m 은 hit한 비율
est
}
mc.hit(m)
```


##control var
```{r conval}
mccontrol <- function(m){
x <- runif(m, 0,0.5)
g <- dcauchy(x)/2
f1 <- x^2
f2 <- x^4
muf1 <- 1/12
muf2 <- 1/80
L <- lm(g~f1+f2)
#est <- mean(g) - L$coeff[2]*(mean(f1)-muf2) - L$coeff[3]*(mean(f2)-muf2)
est2 <- sum(lm(g ~ f1+f2)$coeff*c(1, muf1, muf2))
est2
}
mccontrol(m)
```

##var 비교
```{r vs_var}
set.seed(1)
rep11 <- foreach(i=1:100, .combine = bind_rows) %do%
               { 
                 tibble(MC1=mc(m),
                 MC21=mc.impo1(m),
                 MC22=mc.impo2(m),
                 MC3=mc.hit(m),
                 MC4=mccontrol(m))
} %>% 
  summarise(base_vs_impo1=sd(MC1)^2/sd(MC21)^2,
            base_vs_impo2=sd(MC1)^2/sd(MC22)^2,
            base_vs_hit=sd(MC1)^2/sd(MC3)^2,
            base_vs_conval=sd(MC1)^2/sd(MC4)^2)



(resault4 <- rep11)
```
